Efficient Coalition Formation \\ for Web Services

### 2013-12-19 papers/coalition-journal-R0-Submitted/coalition_journal_Ehsan_Final (1).tex
changes

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of average marginal contribution
they add to the coalition. It checks the contribution of member $i$ by adding the agent, to all possible subsets 
of coalitions $S$, where ${S \subseteq N\left\backslash\left\{i\right\}$. If he is added to the set $S$, his 
contribution to the coalition is $v(S \cup \left\{i\right\}) - v(S)$. Average marginal contribution of agent $i$'s 
is calculated by averaging this value over all possible subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).

>>>>

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of average marginal
contribution they add to the coalition. It checks the contribution
of member $i$ by adding the agent, to all possible subsets of
coalitions $S$, where $S \subseteq N-\{i\}$. If he is added to the
set $S$, his contribution to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$. Average marginal contribution of agent
$i$'s is calculated by averaging this value over all possible
subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).

### 2013-12-19 papers/coalition-journal-R0-Submitted/coalition_journal_Ehsan_Final.tex
changes

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of average marginal
contribution they add to the coalition. It checks the contribution
of member $i$ by adding the agent, to all possible subsets of
coalitions $S$, where $S \subseteq N-\{i\}$. If he is added to the
set $S$, his contribution to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$. Average marginal contribution of agent
$i$'s is calculated by averaging this value over all possible
subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).

>>>>

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of marginal contribution
they have to the coalition.

### 2013-12-19 papers/coalition-journal-R0-Submitted/coalition_journal_Rabeb.tex
changes

\subsection{Cooperative Game Concepts}
Cooperative game is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players which can form a group called a $coalition$. A
\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
coalition to a real number $v(N)$, the worth of $N$. This number
usually represents the output or payoff or again the performance
of these players working together as coalition.  If a coalition
$S$ is formed, then it can divide its worth, $v(N)$ in any
possible way among its members. The payoff vector $x \in
\mathbb{R}^N$ is the amount of payoff being distributed among the
members of the coalition $N$. The payoff vector satisfies two
conditions:

\begin{itemize}
    \item $x_i \geq 0$ for all $i \in N$, and
    \item $\sum_{i \in N} x_i \leq v(N)$
\end{itemize}

The second criteria is called the \emph{feasibility} condition,
according to which, the payoff for each agent cannot be more than
the coalition total gain. A payoff vector is also \emph{efficient}
if the payoff obtained by a coalition is distributed amongst the
coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
the characteristic function works in \emph{transferable utility}
(TU) settings, where utility (i.e., payoff) is transferable from
one player to another, or in other words, players have common
currency and a unit of income that is worth the same for all players
\cite{myerson1991game}.

>>>>

\subsection{Cooperative Game Concepts}
Cooperative game is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players. Any
subset $S$ of $N$ can form a group called $coalition$. A
\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
coalition to a real number $v(S)$, the worth of $S$. This number
usually represents the output or payoff or again the performance
of these players working together as coalition.  If a coalition
$S$ is formed, then it can divide its worth, $v(S)$ in any
possible way among its members. The payoff vector $x \in
\mathbb{R}^S$ is the amount of payoff being distributed among the
members of the coalition $S$. The payoff vector satisfies two
conditions:

\begin{itemize}
    \item $x_i \geq 0$ for all $i \in S$, and
    \item $\sum_{i \in S} x_i \leq v(S)$
\end{itemize}

The second criteria is called the \emph{feasibility} condition,
according to which, the payoff for each agent cannot be more than
the coalition total gain. A payoff vector is also \emph{efficient}
if the payoff obtained by a coalition is distributed amongst the
coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
the characteristic function works in \emph{transferable utility}
(TU) settings, where utility (i.e., payoff) is transferable from
one player to another, or in other words, players have common
currency and a unit of income that is worth the same for all players
\cite{myerson1991game}.
